Augraphy: A Data Augmentation Library for Document Images

### 2023-02-11 paper.tex
Minor updates

\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into pipeline objects which carry out the image manipulation.
Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.

>>>>

\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into pipeline objects which carry out the image manipulation.
Users of the library can define directed acyclic graphs of images and their transformations via the \texttt{AugraphyPipeline} API, representing the passage of a document through real-world alterations.
